---
title: "Alcohol vs Seat choice"
author: "Matias Lucha"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
# Introduction
Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in?

The data came from UCDavis in the year
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks consumed and the row people sit in.

$H_A$: There is a difference between number of drinks and row for at least two rows.

#Methods: 
In the data set davisdata. Seat is a categorical variable and alcohol is numerical.

we try to predict alcohol ~ Seat so we use the Num ~ Cat

# Results

## Descriptive Results

### Graphical summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This box plot shows that the further from the front (middle to back), the higher values we get for alcohol consumptions.

### Numerical summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The numerical summary shows that as you go further in seating, the amount (median) of alcohol consumption increases. 


### Inferential Results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value of this anova test is 0.000116 which is less than 0.05, therefore we reject the null hypothesis.
Therefore, there is a difference in alcohol consumption and where a person may sit depending on row. 

## When significant follow up with TukeyHSD
```{r}
plot(TukeyHSD(model1))
```


## Conclusions

Due to the p-value being less than 0.05, at 0.000116 

