---
title: "Alcohol vs Seat choice"
author: "Matias Lucha"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
# Introduction
Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in?

The data came from UCDavis in the year
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks consumed and the row people sit in.

$H_A$: There is a difference between number of drinks and row for at least two rows.

#Methods: 
In the data set davisdata. Seat is a categorical variable and alcohol is numerical.

we try to predict alcohol ~ Seat so we use the Num ~ Cat

# Results

## Descriptive Results

### Graphical summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This box plot shows that the further from the front (middle to back), the higher values we get for alcohol consumptions.

### Numerical summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The numerical summary shows that as you go further in seating, the amount (median) of alcohol consumption increases. 


### Inferential Results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value of this anova test is 0.000116 which is less than 0.05, therefore we reject the null hypothesis.
Therefore, there is a difference in alcohol consumption and where a person may sit depending on row. 

## When significant follow up with TukeyHSD
```{r}
plot(TukeyHSD(model1))
```

From the middle to the front, there is a 0 statistical difference in alcohol consumption from those who sit in the middle to those who sit in the front. However, there is a difference in alcohol consumption from the front and back rows, and the middle and back rows. 
## Conclusions

Due to the p-value being less than 0.05, at 0.000116, we reject the null hypothesis, and therefore alcohol consumption is dependent on where someone may sit. There is a difference between alcohol consumption and those who sit in the front row to the back row, as well as the middle row to the back row. There is no statistical difference in consumption from the front row to the middle row.

