---
title: "Alcohol vs Seat choice"
author: "Matias Lucha"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
# Introduction
Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in?

The data came from UCDavis in the year
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks consumed and the row people sit in.

$H_A$: There is a difference between number of drinks and row for at least two rows.

#Methods: 
In the data set davisdata. Seat is a categorical variable and alcohol is numerical.

we try to predict alcohol ~ Seat so we use the Num ~ Cat

# Results

## Descriptive Results

### Graphical summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
This box plot shows that the further from the front (middle to back), the higher values we get for alcohol consumptions.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


